State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources

### 2020-08-07 analysis/paper/appendices/Appendix_STADEM_descrip.Rmd
changed "log" to "ln" per AFS journal instructions

$$
\begin{aligned}
  \log \left( X_{t} \right) &= \log \left( X_{t-1} \right) + e_t \\
  e_t &\sim \mathcal{N}(0, \sigma^2_X)
\end{aligned}
$$

@@

$$
\begin{aligned}
  \left( Y^T_{w,t}, Y^T_{h,t}, Y^T_{hnc,t} \right) &\sim \text{Multinom} \left( \omega_t, Y^T_t \right) \\
  \omega_t &= \frac{\exp(\phi_t)}{\sum{\exp(\phi_t})} \\
  \phi_{w,t} &= \log \left( \frac{\omega_{w,t}}{\omega_{h,t}} \right) \\
  \phi_{hnc,t} &= \log \left( \frac{\omega_{hnc,t}}{\omega_{h,t}} \right) \\
  \phi_{h,t} &= 0 \\
  \phi_{w,t} &= \phi_{w, t-1} + d_{w,t} \\
  \phi_{hnc,t} &= \phi_{hnc, t-1} + d_{hnc,t} \\
  d_t &\sim \mathcal{N}(0, \sigma^2_\omega) \\
\end{aligned}
$$

@@

The model was fit using the JAGS program [@R-rjags], run with R software [@R-Core-Team2020]. Uninformative priors were used for $\sigma_X, \sigma_\eta, \sigma_\theta, \sigma_\omega$ and $\log(X_1)$ (Uniform(0,10)), as well as logit($\eta_1$) and logit($\theta_1$) ($\mathcal{N}(0, 1000)$), and finally $\phi_{w,1}$ and $\phi_{hnc,1}$ ($\mathcal{N}(0, 100)$).

>>>>

$$
\begin{aligned}
  \ln \left( X_{t} \right) &= \ln \left( X_{t-1} \right) + e_t \\
  e_t &\sim \mathcal{N}(0, \sigma^2_X)
\end{aligned}
$$

@@

$$
\begin{aligned}
  \left( Y^T_{w,t}, Y^T_{h,t}, Y^T_{hnc,t} \right) &\sim \text{Multinom} \left( \omega_t, Y^T_t \right) \\
  \omega_t &= \frac{\exp(\phi_t)}{\sum{\exp(\phi_t})} \\
  \phi_{w,t} &= \ln \left( \frac{\omega_{w,t}}{\omega_{h,t}} \right) \\
  \phi_{hnc,t} &= \ln \left( \frac{\omega_{hnc,t}}{\omega_{h,t}} \right) \\
  \phi_{h,t} &= 0 \\
  \phi_{w,t} &= \phi_{w, t-1} + d_{w,t} \\
  \phi_{hnc,t} &= \phi_{hnc, t-1} + d_{hnc,t} \\
  d_t &\sim \mathcal{N}(0, \sigma^2_\omega) \\
\end{aligned}
$$

@@

The model was fit using the JAGS program [@R-rjags], run with R software [@R-Core-Team2020]. Uninformative priors were used for $\sigma_X, \sigma_\eta, \sigma_\theta, \sigma_\omega$ and $\ln(X_1)$ (Uniform(0,10)), as well as logit($\eta_1$) and logit($\theta_1$) ($\mathcal{N}(0, 1000)$), and finally $\phi_{w,1}$ and $\phi_{hnc,1}$ ($\mathcal{N}(0, 100)$).
